Semi-permeable vesicles: mathematical formulation, numerics and physics

### 2019-04-12 vesicle_code/docs/permeableVes/main.tex
Updated the A matrix
Figures for parameter sweeps (Chi, beta, and RA) added to main TeX.

\documentclass[aps,prl,twocolumn,showpacs]{revtex4}
\usepackage{amsmath,amsfonts,bm, color}
\usepackage{graphicx,epsfig}
%\input vs_macros.tex
%Dfig puts a figure of specified size at the place indicated.
\newcommand{\Dfig}[2]{\epsfig{figure=#1,width=#2cm}}

@@

\section{Numerics}
To address stiffness associated with high-order derivatives,
equation~\eqref{eqn:vesVelocity} is discretized with a semi-implicit
time stepping method similar to our previous works.  First, we introduce
the notation
\begin{align}
  B[\mbx]\mbf &= -\kappa_b\frac{d^4}{ds^4} \mbf, \\
  T[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
  P[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn, \\
  D[\mbx]\mbf &= \mbx_s \cdot \mbf_s
\end{align}
where $\mbn$ is the is the outward unit normal of the vesicle
parameterized by $\mbx$, and $d/ds$ is its arclength derivative.
Dropping the dependence of the operators on $\mbx$, the dynamics of the
vesicle are governed by
\begin{align}
  \dot{\mbx} &= \mbu_{\infty}(\mbx) + 
  \beta P(B\mbx + T\sigma) + \sgl(B\mbx + T\sigma), \\
  D \dot{\mbx} &= 0.
\end{align}
Using the notation $B^N$ to denote the bending operator due to the
vesicle configuration at time $t_N$, and similar notation for the other
operators, we apply the semi-implicit time stepping method
\begin{multline}  
  \frac{\mbx^{N+1} - \mbx^N}{\Delta t} = \mbu_\infty(\mbx^N) 
  + \beta P^N(B^N\mbx^{N+1} + T^N\sigma^{N+1})  \\
  + \sgl^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}).
\end{multline}
Applying $D$ to the first-order time discretization of
equation~\eqref{eqn:vesVelocity}, the inextensibility condition is
\begin{align*}
  &D^N(\mbx^{N+1} - \mbx^N) = 0 \\ 
  \Rightarrow &D^N\mbx^{N+1} = D^N \mbx^N \\ 
  \Rightarrow &D^N\mbx^{N+1} = 1.
\end{align*}
Finally, we write the time stepping method in matrix form as
\begin{align}
  A \left(
    \begin{array}{c}
      \mbx^{N+1} \\ \sigma^{N+1}
    \end{array}
  \right) = 
  \left(
    \begin{array}{c}
      \mbx^{N} + \Delta t \mbu_\infty(\mbx^N) \\ \mathbf{1}
    \end{array}
  \right),
\end{align}
where
\beq
 A = \left(
  \begin{array}{cc}
    I - \Delta t \beta P^N - \Delta t \sgl^N B^N & 
    -\Delta t P^N T^N - \Delta t \sgl^N T^N \\
    D^N & 0
  \end{array}
  \right).
\eeq

%We obtain the matrix
%\begin{multline}
% \begin{pmatrix}
% 	\mbx^N \\ \textbf{1} 
% \end{pmatrix} = \\
%\begin{pmatrix}
%	I - \Delta t \sgl^N\mathcal{B}^N - \Delta t \beta \mathcal{P}^N\mathcal{B}^N & -\Delta t \sgl^N \mathcal{T}^N-\Delta t\beta \mathcal{P}^N\mathcal{T}^N \\ & \textbf{0}
%\end{pmatrix}
%\begin{pmatrix}
%	\mbx^{N+1} \\ \sigma^{N+1}
%\end{pmatrix} 
%\end{multline}

>>>>

\documentclass[aps,prl,showpacs]{revtex4}
\usepackage{amsmath,amsfonts,bm, color}
\usepackage{graphicx,epsfig}
%\input vs_macros.tex
%Dfig puts a figure of specified size at the place indicated.
\newcommand{\Dfig}[2]{\epsfig{figure=#1,width=#2cm}}

@@

\section{Numerics}
To address stiffness associated with high-order derivatives,
equation~\eqref{eqn:vesVelocity} is discretized with a semi-implicit
time stepping method similar to our previous works.  First, we introduce
the notation
\begin{align}
  B[\mbx]\mbf &= -\kappa_b\frac{d^4}{ds^4} \mbf, \\
  T[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
  P[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn, \\
  D[\mbx]\mbf &= \mbx_s \cdot \mbf_s
\end{align}
where $\mbn$ is the is the outward unit normal of the vesicle
parameterized by $\mbx$, and $d/ds$ is its arclength derivative.
Dropping the dependence of the operators on $\mbx$, the dynamics of the
vesicle are governed by
\begin{align}
  \dot{\mbx} &= \mbu_{\infty}(\mbx) + 
  \beta P(B\mbx + T\sigma) + \sgl(B\mbx + T\sigma), \\
  D \dot{\mbx} &= 0.
\end{align}
Using the notation $B^N$ to denote the bending operator due to the
vesicle configuration at time $t_N$, and similar notation for the other
operators, we apply the semi-implicit time stepping method
\begin{multline}  
  \frac{\mbx^{N+1} - \mbx^N}{\Delta t} = \mbu_\infty(\mbx^N) 
  + \beta P^N(B^N\mbx^{N+1} + T^N\sigma^{N+1})  \\
  + \sgl^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}).
\end{multline}
Applying $D$ to the first-order time discretization of
equation~\eqref{eqn:vesVelocity}, the inextensibility condition is
\begin{align*}
  &D^N(\mbx^{N+1} - \mbx^N) = 0 \\ 
  \Rightarrow &D^N\mbx^{N+1} = D^N \mbx^N \\ 
  \Rightarrow &D^N\mbx^{N+1} = 1.
\end{align*}
Finally, we write the time stepping method in matrix form as
\begin{align}
  A \left(
    \begin{array}{c}
      \mbx^{N+1} \\ \sigma^{N+1}
    \end{array}
  \right) = 
  \left(
    \begin{array}{c}
      \mbx^{N} + \Delta t \mbu_\infty(\mbx^N) \\ \mathbf{1}
    \end{array}
  \right),
\end{align}
where
\beq
 A = \left(
  \begin{array}{cc}
    I + \Delta t \beta P^N B^N + \Delta t \sgl^N B^N & 
    -\Delta t P^N T^N - \Delta t \sgl^N T^N \\
    D^N & 0
  \end{array}
  \right).
\eeq

\begin{figure}
	\centering
	\includegraphics[width=.9\textwidth]{figures/1.jpg}
	\includegraphics[width=.9\textwidth]{figures/2.jpg}
	\includegraphics[width=.9\textwidth]{figures/3.jpg}
	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
	\label{Shear0}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=.9\textwidth]{figures/4.jpg}
	\includegraphics[width=.9\textwidth]{figures/5.jpg}
	\includegraphics[width=.9\textwidth]{figures/6.jpg}
	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
	\label{Shear0}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=.9\textwidth]{figures/7.jpg}
	\includegraphics[width=.9\textwidth]{figures/8.jpg}
	\includegraphics[width=.9\textwidth]{figures/9.jpg}
	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
	\label{Shear0}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=.9\textwidth]{figures/10.jpg}
	\includegraphics[width=.9\textwidth]{figures/11.jpg}
	\includegraphics[width=.9\textwidth]{figures/12.jpg}
	\caption{Reduced area as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
	\label{Shear0}
\end{figure}

 \begin{figure}
 	\centering
 	\includegraphics[width=.9\textwidth]{figures/BE1.jpg}
 	\includegraphics[width=.9\textwidth]{figures/BE2.jpg}
 	\includegraphics[width=.9\textwidth]{figures/BE3.jpg}
 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0$.}
 	\label{Shear0}
 \end{figure}

 \begin{figure}
 	\centering
 	\includegraphics[width=.9\textwidth]{figures/BE4.jpg}
 	\includegraphics[width=.9\textwidth]{figures/BE5.jpg}
 	\includegraphics[width=.9\textwidth]{figures/BE6.jpg}
 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 0.5$.}
 	\label{Shear0}
 \end{figure}

 \begin{figure}
 	\centering
 	\includegraphics[width=.9\textwidth]{figures/BE7.jpg}
 	\includegraphics[width=.9\textwidth]{figures/BE8.jpg}
 	\includegraphics[width=.9\textwidth]{figures/BE9.jpg}
 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 1$.}
 	\label{Shear0}
 \end{figure}

 \begin{figure}
 	\centering
 	\includegraphics[width=.9\textwidth]{figures/BE10.jpg}
 	\includegraphics[width=.9\textwidth]{figures/BE11.jpg}
 	\includegraphics[width=.9\textwidth]{figures/BE12.jpg}
 	\caption{Bending energy as a function of time for $\beta = [0, 10^{-2},10^{-1}, 1]$ with a shear flow rate $\chi = 2$.}
 	\label{Shear0}
 \end{figure}
